The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multiphase Forest Inventories

### 2018-11-11 revision/reviews.tex
update 11_11_2018
update 11_11_2018

\title{Reviews}

@@

\answerfin{The reviewer makes a valid point that it would be easier from a "plug-and-play" perspective to simply interpret what the phase memberships were via the locations of NAs. However, NAs in covariates may have nothing to do with the sampling design e.g. non-response due to inaccessibility or lidar error. We feel that the current implementation of phase\_id forces the user to be more attentive when these situations occur that may interfere with the uniform and independent sampling assumption for the sampling design.  To assist the user in understanding how function calls are made we have included several examples for the usage of all estimators in both the documentation and the vignette using real-life examples.  It should also be noted that defining the phase\_id for all observations with the same (terrestrial) id essentially does the same as the reviewer has described with a warning message given.  However we do not recommend this usage for the aforementioned reasons.}
\\

My main concern is that the limitations of the methodology are nowhere clearly specified in the manuscript. On page 5, it is suggested that a consequence of the design-based approach "is that the estimation properties of design-based regression estimators (e. g. unbiasedness) typically hold regardless of the model that is chosen." While this is basically true for unbiasedness, unbiasedness by itself means little, and, more important, the statement does not extend to relevant properties such as coverage rates of confidence intervals. Indeed, if s2 contains less than 1-$\alpha$ of the entire population, any true 1-$\alpha$ confidence interval for the population mean necessarily involves distributional assumptions about the population because otherwise any fixed Y(x0), which has probability > $\alpha$ of not being included in the sample, can be anything, so any conclusion about the mean would be wrong with probability > $\alpha$. (Similarly, with the infinite population approach, one needs assumptions on the tails.) Of course, it is very plausible that such issues go away once reasonable assumptions (suitable sample sizes etc.) are met. While this will be obvious in some situations, I expect many potential uses of the package where this is less so, either because users are specifically looking at edge cases in search of interesting phenomena or, more commonly, because there really is very little data available - the typical situation for a forestry undergraduate writing a thesis. The vague invocation of the central limit theorem (page 24) won't help here. Below I include three numerical examples where the nominal 95\% confidence intervals never exceed a coverage of 85\%.\\

\answerfin{The reviewer is concerned that more attention needs to be given concerning issues in boundary cases with the coverage rates.  The given explanation seems to have switched $\alpha$ and $1-\alpha$ in a few places but made clear that there was a link between too low sampling fractions and coverage rates under the finite population approach.  However, the concept of having a sampling fraction too low for the confidence level isn't really applicable in the infinite population approach where the total population is a continuum of points and is thus infinity.  We have performed simulations under the infinite population approach and could not reproduce the reviewers examples, but did show that extremely low sample sizes could have an influence.  The cited literature includes many simulations and artificial examples demonstrating the distribution of the parameter of interest (the integral of the local density function) is beyond analytical treatment under the sampling schemes but can be well approximated by t-distribution (and consequently the normal in large samples). The reviewer does have a very valid point that discussing coverage rates would improve the paper. For this reason we have expanded the confidence interval section to include some new simulated examples of coverage rates to develop the reader's intuition about when the sample size is too low to produce reliable results.}
\\

As I personally regard solid knowledge of the limitations of a statistical method as a prerequisite of its use in science and in addition believe it would help many potential users of the package, I ask the authors to consider adding some clarification regarding typical situations where the methods can be or should not be applied. For example, showing a few artificial test cases highlighting the most important requirements would probably not be difficult.\\

@@

Also section 5 on CIs could be considerably shortened. Needs to be a section on its own right? Sections 6 and 7 are very interesting but the R code under 7.1 could probably be condensed a lot.\\
\\
\answerfin{Reader 1 suggested that this section in fact be extended to include discussion about coverage rates.  We prefer to go in this direction.} \\

@@

\answerfin{The population doesn't need to be tessellated and can be allowed to overlap or not use all the wall-to-wall map in the infinite population approach. This is already mentioned on page 9.  Section 2.1 discusses the Infinite Population Approach.  Some brief discussion comparing to the finite is included, but as this package is about software written for the infinite not finite approach, we prefer not to delve too deeply into a topic that makes little practical difference.} \\

@@

\answerfin{The estimators presented in our article particularly rely on the assumption that the forest area $\lambda$ is known. The exact forest area is only needed to compute the total by multiplying, e.g., the sample mean with $\lambda(F)$. The author is, however, right by saying that in most NFIs the forest area is rather estimated than known exactly. A solution, as applied in the Swiss NFI, is to estimate the forest area by multiplying the \textit{known} country area by the percentage of (independent and uniformly distributed) sample points falling within the forest (decision made by field crews) -> see Mandallaz 2014: Note on the estimation of totals. So actually, its no big deal "to do it in the infinite population approach" but how the user wants to estimate forest area is up to them.  A citation noting where the reader can find more information on this topic has been included but further discussion was not included as it was outside the scope of this paper.}

% --------------------------- %

@@

\answerfin{The extended synthetic estimator does not necessarily need to implement an ancova model.  That depends on the types of variables that the user has specified.  The extended synthetic estimator merely adds an indicator variable for the small area in addition to the other variables that the user specified. This can in fact extend the model to an ancova model if the explanatory variables contain at least one continuous predictor. However, the reason of adding the indicator variable exclusively is to ensure the zero-mean-residual property in both the global domain F and small area G, and not to improve the model fit. We think that linking the indicator variable to the anova or ancova modeling technique might probably cause misunderstanding of the indicator purpose on the side of the readers.}
% --------------------------- %

>>>>

\title{Answer to Reviewers}

@@

\answerfin{The reviewer makes a valid point that it would be easier from a "plug-and-play" perspective to simply interpret what the phase memberships were via the locations of NAs. However, NAs in covariates may have nothing to do with the sampling design e.g. non-response due to inaccessibility or sensor failures (see e.g. Hill, A., Mandallaz, D., \& Langshausen, J. (2018). A Double-Sampling Extension of the German National Forest Inventory for Design-Based Small Area Estimation on Forest District Levels. \textit{Remote Sensing}, 10(7), 1052.). We feel that the current implementation of phase\_id forces the user to be more attentive when these situations occur that may interfere with the uniform and independent sampling assumption for the sampling design.  To assist the user in understanding how function calls are made we have included several examples for the usage of all estimators in both the documentation and the vignette using real-life examples.  It should also be noted that defining the phase\_id for all observations with the same (terrestrial) id essentially does the same as the reviewer has described with a warning message given.  However we do not recommend this usage for the aforementioned reasons.}
\\

My main concern is that the limitations of the methodology are nowhere clearly specified in the manuscript. On page 5, it is suggested that a consequence of the design-based approach is that 'the estimation properties of design-based regression estimators (e. g. unbiasedness) typically hold regardless of the model that is chosen.' While this is basically true for unbiasedness, unbiasedness by itself means little, and, more important, the statement does not extend to relevant properties such as coverage rates of confidence intervals. Indeed, if s2 contains less than 1-$\alpha$ of the entire population, any true 1-$\alpha$ confidence interval for the population mean necessarily involves distributional assumptions about the population because otherwise any fixed Y(x0), which has probability > $\alpha$ of not being included in the sample, can be anything, so any conclusion about the mean would be wrong with probability > $\alpha$. (Similarly, with the infinite population approach, one needs assumptions on the tails.) Of course, it is very plausible that such issues go away once reasonable assumptions (suitable sample sizes etc.) are met. While this will be obvious in some situations, I expect many potential uses of the package where this is less so, either because users are specifically looking at edge cases in search of interesting phenomena or, more commonly, because there really is very little data available - the typical situation for a forestry undergraduate writing a thesis. The vague invocation of the central limit theorem (page 24) won't help here. Below I include three numerical examples where the nominal 95\% confidence intervals never exceed a coverage of 85\%. As I personally regard solid knowledge of the limitations of a statistical method as a prerequisite of its use in science and in addition believe it would help many potential users of the package, I ask the authors to consider adding some clarification regarding typical situations where the methods can be or should not be applied. For example, showing a few artificial test cases highlighting the most important requirements would probably not be difficult.\\

\answerfin{The reviewer is concerned that more attention needs to be given concerning issues in boundary cases with the coverage rates.  The given explanation seems to have switched $\alpha$ and $1-\alpha$ in a few places but made clear that there was a link between too low sampling fractions and coverage rates under the finite population approach.  However, the concept of having a sampling fraction too low for the confidence level isn't really applicable in the infinite population approach where the total population is a continuum of points and is thus infinity.  We have performed simulations under the infinite population approach and could not reproduce the reviewer's examples, but did show that extremely low sample sizes could have an influence.  The cited literature includes many simulations and artificial examples demonstrating that the distribution of the parameter of interest (the integral of the local density function) is beyond analytical treatment under the sampling schemes but can be well approximated by the \textit{t}-distribution (and consequently the normal distribution in large samples). The reviewer does have a very valid point that discussing coverage rates would improve the paper. For this reason we have expanded the confidence interval section to include some new simulated examples of coverage rates to develop the reader's intuition about when the sample size is too low to produce reliable results.}
\\

@@

Also section 5 on CIs could be considerably shortened. Needs to be a section on its own right? Sections 6 and 7 are very interesting but the R code under 7.1 could probably be condensed a lot.\\
\\
\answerfin{Reader 1 suggested that this section should in fact be extended to include discussion about coverage rates.  We prefer to go in this direction.} \\

@@

\answerfin{The population doesn't need to be tessellated and can be allowed to overlap or not use all the wall-to-wall map information in the infinite population approach. This is already mentioned on page 9.  Section 2.1 discusses the Infinite Population Approach.  Some brief discussion comparing to the finite is included, but as this package is about software written for the infinite not finite approach, we prefer not to delve too deeply into a topic that makes little practical difference.} \\

@@

\answerfin{The estimators presented in our article particularly rely on the assumption that the forest area $\lambda$ is known. The exact forest area is only needed to compute the total by multiplying, e.g., the sample mean with $\lambda(F)$. The author is, however, right by saying that in most NFIs the forest area is rather estimated than known exactly. A solution, as applied in the Swiss NFI, is to estimate the forest area by multiplying the \textit{known} country area by the percentage of (independent and uniformly distributed) sample points falling within the forest (decision made by field crews). A citation where the reader can find more information on this topic has been included.}
% --------------------------- %

@@

\answerfin{The extended synthetic estimator does not necessarily need to implement an ancova model.  That depends on the types of variables that the user has specified.  The extended synthetic estimator merely adds an indicator variable for the small area in addition to the other variables that the user specified. This can in fact extend the model to an ancova model if the explanatory variables contain at least one continuous predictor. However, the reason of adding the indicator variable is purely to ensure the zero-mean-residual property in both the global domain F and small area G, and not to improve the model fit. We think that linking the indicator variable to the anova or ancova modeling technique might probably cause a misunderstanding of the indicator purpose on the side of the readers.}
% --------------------------- %

### 2018-11-11 rnw/Appendix.Rnw
update 11_11_2018
update 11_11_2018

 \begin{small}
<<eval=FALSE>>= 
# --- run global simulations --- #
library(forstinventory)
global.sims<- data.frame()
n1_sims<- c(250, 500, 750, 1000, 1500, 2000) # n1 sample sizes
  for (i in 1:length(n1_sims)){
    res<- run.global.sim(num_replications = 10000, n1.vec = n1_sims[i])
    global.sims <- rbind(global.sims, res)
  }
@
\end{small}

>>>>

 \begin{small}
<<eval=FALSE>>= 
# --- run global simulations --- #
library(forestinventory)
global.sims<- data.frame()
n1_sims<- c(250, 500, 750, 1000, 1500, 2000) # n1 sample sizes
  for (i in 1:length(n1_sims)){
    res<- run.global.sim(num_replications = 10000, n1.vec = n1_sims[i])
    global.sims <- rbind(global.sims, res)
  }
@
\end{small}

### 2018-11-11 rnw/Calculation of Confidence Intervals.Rnw
update 11_11_2018
update 11_11_2018

A commonly raised question of practitioners regarding the application of design-unbiased estimators is which minimum terrestrial sample size should be provided. Answering this question is highly related to ensuring the validity of the confidence coverage rates by a sufficiently large sample size. It has to be noted that giving a generally valid sample size for the asymptotic validity range is, unfortunately, infeasible because the convergence to the \textit{t}- or normal distribution also depends on the hetereogeneity of the underlying population. However, simulation studies using an artificial local density surface were conducted in \citet{mandallaz2013a} and \citet{mandallaz2013b} to empirically check the asymptotic properties of the estimators. In order to develop the reader's intuition about when the sample size is too low to produce reliable results, we re-evaluated these simulations for a broader range of sample sizes. For each fixed sample size $n_1$ and sampling fraction, 10000 samples $s_2$ were conducted by simple random sampling and the 95\% confidence interval based on the g-weight variance was calculated for each sample after applying the global two-phase estimator (Section \ref{sec:twophase_globest}). The $R^2$ of the regression model was 0.81. For further details on the simulation, the reader is referred to the original articles mentioned above. The results can also be reproduced or expanded using the \proglang{R}-code given in the Appendix.\par

From the simulation example for global estimation (Figure \ref{fig:covrate_sim}) it is obvious that the nominal coverage rate of 95\% can expected to be met for sample sizes larger equals $n_2$=50 regardless of the chosen sample size $n_1$. The realized coverage rate only drops significantly below 90\% if considerably small sampling fractions (i.e., the ratio ${n_2}/{n_1}$) < 0.1 are used that lead to small terrestrial sample sizes of 20 and less. The simulation examples also confirmed that in such cases, one should whenever possible consider one of the design-unbiased small area estimators (P)SMALL or EXT(P)SYNTH for which the nominal coverage rates in the simulations were already met for sample sizes $n_{2,G}$ > 5. Finally, it should also be noted that applying the design-based estimators under systematic sampling will lead to an inflation of the estimated variance \citep{mandallaz1993}. This will also effect the actual coverage rates to be higher than those derived under simple random sampling.

\begin{figure}[h]
\centering
\resizebox{0.80\hsize}{!}{\includegraphics{fig/globalsim.png}}
\caption{Coverage rates realized undervarying sample sizes $n_1$ and sampling fractions for an artificial simulation example given in \citet{mandallaz2013a}. The nominal confidence level was 95\% and for each setup, 10000 simulations were performed using simple random sampling.}
\label{fig:covrate_sim}
\end{figure}

>>>>

A commonly raised question of practitioners regarding the application of design-unbiased estimators is which minimum terrestrial sample size should be provided. Answering this question is highly related to ensuring the validity of the confidence coverage rates by a sufficiently large sample size. It has to be noted that giving a generally valid sample size for the asymptotic validity range is, unfortunately, infeasible because the convergence to the \textit{t}- or normal distribution also depends on the hetereogeneity of the underlying population. However, simulation studies using an artificial local density surface were conducted in \citet{mandallaz2013a} and \citet{mandallaz2013b} to empirically check the asymptotic properties of the estimators. In order to develop the reader's intuition about when the sample size is too low to produce reliable results, we re-evaluated these simulations for a broader range of sample sizes. For each fixed sample size $n_1$ and sampling fraction, 10000 samples were conducted by simple random sampling and the 95\% confidence interval based on the g-weight variance was calculated for each sample after applying the global two-phase estimator (Section \ref{sec:twophase_globest}). The $R^2$ of the regression model was 0.81. For further details on the simulation, the reader is referred to the original articles mentioned above. The results can also be reproduced or expanded using the \proglang{R}-code given in the Appendix.\par

From the simulation example for global estimation (Figure \ref{fig:covrate_sim}) it is obvious that the nominal coverage rate of 95\% can expected to be met for large sample sizes (e.g., $n_2$=50) regardless of the chosen sample size $n_1$. The realized coverage rate only drops significantly below 90\% if considerably small sampling fractions (i.e., the ratio ${n_2}/{n_1}$) < 0.1 are used that lead to small terrestrial sample sizes of 20 and less. The simulation examples also confirmed that in such cases, one should whenever possible consider one of the design-unbiased small area estimators (P)SMALL or EXT(P)SYNTH for which the nominal coverage rates in the simulations were already met for sample sizes $n_{2,G}$ > 5. Finally, it should also be noted that applying the design-based estimators under systematic sampling will lead to an inflation of the estimated variance \citep{mandallaz1993}. This will also effect the actual coverage rates to be higher than those derived under simple random sampling.

\begin{figure}[h]
\centering
\resizebox{0.80\hsize}{!}{\includegraphics{fig/globalsim.png}}
\caption{Coverage rates realized under varying sample sizes $n_1$ and sampling fractions for an artificial simulation example given in \citet{mandallaz2013a}. The nominal confidence level was 95\% and for each setup, 10000 simulations were performed using simple random sampling.}
\label{fig:covrate_sim}
\end{figure}
